ropenblas: Download, Compile and Link OpenBLAS Library with R

### 2020-10-01 paper/paper.Rmd
update

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'ropenblas: Download, Compile and Link OpenBLAS Library with R'
tags:
  - R
  - BLAS
  - Compiling R
  - Compiling OpenBLAS
  - Link OpenBLAS
authors:
  - name: Pedro Rafael Diniz Marinho
    orcid: 0000-0003-1591-8300
    affiliation: 1
affiliations:
 - name: Department of Statistics, Federal University of Paraíba, João Pessoa, Paraíba - PB, Brazil
   index: 1
citation_author: Marinho
date: "`r Sys.Date()`"
year: "`r format(Sys.Date(), '%Y')`"
bibliography: paper.bib
output: rticles::joss_article
header-includes:
  - \usepackage{float}
csl: apa.csl
journal: JOSS
---

@@

The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU / Linux systems without depending on the distribution repositories. This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion. The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU / Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R. All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.

>>>>

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'ropenblas: Download, Compile and Link OpenBLAS Library with R'
tags:
  - R
  - Compiling R and OpenBLAS
  - Link OpenBLAS
  - Switch between versions of R
  - Fast algebraic computing
authors:
  - name: Pedro Rafael Diniz Marinho
    orcid: 0000-0003-1591-8300
    affiliation: 1
affiliations:
 - name: Department of Statistics, Federal University of Paraíba, João Pessoa, Paraíba - PB, Brazil
   index: 1
citation_author: Marinho
date: "`r Sys.Date()`"
year: "`r format(Sys.Date(), '%Y')`"
bibliography: paper.bib
output: rticles::joss_article
header-includes:
  - \usepackage{float}
csl: apa.csl
journal: JOSS
---

@@

The `ropenblas` package aims to allow algebraic computing of R to be performed using the OpenBLAS library, that is, it allows easy linking of R to the OpenBLAS library on GNU/Linux systems without depending on the distribution repositories. This will allow several researches in the areas of statistics, data science and machine learning to take advantage of a more efficient performance in algebraic calculations, for example, multiplication, factorization and matrix inversion. The `ropenblas` library, version 0.2.8 will also allow the R programmer to have, in his GNU/Linux distribution, several compiled versions of the R language giving the possibility to easily switch between these versions, this being an Open Source functionality that is only possible in some commercial IDEs of R. All this is done within the R language, minimizing the chance of less experienced users to break their operating system by running several instructions that are not perfectly understood.
